Fitting convex polyhedra to project 2D bounding box

### 2015-05-04 Paper/suplementarymaterial.tex
Latest version of presentation.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
%%%%%%%%%%% CVPR template packages end %%%%%%%%%%%%%%
\usepackage{verbatim} % for comment environment
% \usepackage{soul} % for \hl highlighting
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{489} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\DeclareMathOperator{\diag}{diag}

% 3D pose of the cars and ego motion
\newcommand{\uv}[1]{\hat{\mathbf{#1}}}
\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}

% ego pose
\newcommand{\egop}[1][t]{\pos{c}{#1}}
\newcommand{\egoo}[1][t]{\ori{c}{#1}}
\newcommand{\egos}[1][t]{\state{c}{#1}}

% relative pose between camera and car $i$
\newcommand{\relp}[2]{\Omega^{#1}(#2)}
\newcommand{\relpz}[2]{\Omega_z^{#1}(#2)}

% 3D tracks on car $i$ in its own coordinate frame
\newcommand{\tracklets}{\mathbf{X}^{(i)}_o}
\newcommand{\tracklet}[1]{\mathbf{x}^{(i)}_{#1}}
% track projections on camera
\newcommand{\trackp}[1]{\mathbf{u}^{(i)}(#1)}
\newcommand{\trackpj}[1]{\mathbf{u}_j(#1)}
% Unclassified track point projected on camera
\newcommand{\ucTrackp}{\mathbf{u}(t)}

% dimensions of car $i$
\newcommand{\dimsn}[1]{\mathbf{B}^{#1}}
\newcommand{\expDimsn}{\hat{\mathbf{B}}}

% projection function
\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}\left(#1\right)}
\newcommand{\projectionOft}[1]{\pi_{\relp{i}{t+1}}\left(#1\right)}
\newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
\newcommand{\cornerProj}[1]{\pi^{#1}_{\relp{i}{t}}(\dimsn{i})}
\newcommand{\triangleProj}[1]{\triangle^{#1}_{\relp{i}{t}}(\dimsn{i})}

% bounding box corners on image
\newcommand{\bb}[1]{\mathbf{d}^{#1}(t)}

\newcommand{\Energy}[1]{\mathcal{E}^{it}_{\text{#1}}}
\newcommand{\pEnergy}[1]{\mathcal{E}^{ijt}_{\text{#1}}}
% Weighted energy
\newcommand{\WEnergy}[1]{\lambda_{\text{#1}}\Energy{#1}}
\newcommand{\EnergyCol}{\mathcal{E}^{ijt}_{\text{col}}}
\newcommand{\WEnergyCol}{\lambda_{\text{col}}\EnergyCol}

\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
\newcommand{\minx}{x_{\text{min}}}
\newcommand{\miny}{y_{\text{min}}}
\newcommand{\maxx}{x_{\text{max}}}
\newcommand{\maxy}{y_{\text{max}}}
\newcommand{\frontface}{F^i_\text{FF}(t)}

\newcommand{\occ}[1]{o({#1})}
\newcommand{\face}{F^i_k(t)}

\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
\newcommand{\occft}[1]{f_{occ}(#1)}

\newcommand{\ray}{\hat{\mathbf{r}}_j}
\newcommand{\occfray}{f_{occ}(\lambda\ray)}
\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}

\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\assocP}{a^{(ij)}(\lambda)}
\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}

\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
\newcommand{\dishort}{d_i(\mathbf{x})}

\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}

\newcommand{\Gauss}{\mathcal{N}}
\newcommand{\PropDist}{\mathcal{W}_j}

\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}

\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}

\newcommand{\muit}{\mu^(i)_t}
\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}

\newcommand{\muic}{{\mu^(i)_c}}
\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}

\newcommand{\muiu}{\mu^{(i)}_t}
\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}

\newcommand{\xt}{\mathbf{x}_t}
\newcommand{\xc}{\mathbf{x}_c}

\newcommand{\Rctot}{R}
\newcommand{\tctot}{t}

\newcommand{\tcmut}{t'}

\newcommand{\Beizer}{B\'eizer }

\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}

\newcommand{\xymin}[1]{#1_{\text{min}}}
\newcommand{\xymax}[1]{#1_{\text{max}}}
\newcommand{\xmin}{\xymin{x}}
\newcommand{\xmax}{\xymax{x}}
\newcommand{\ymin}{\xymin{y}}
\newcommand{\ymax}{\xymax{y}}
\newcommand{\Tr}[3]{{}^{#1}{#2}_{#3}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
%\setcounter{page}{4321}
%\DeclareMathSymbol{\Tangent}
\DeclareMathOperator{\sech}{sech}
\DeclareMathOperator{\poly}{poly}
\DeclareMathOperator*{\argmin}{\arg\min}

\begin{document}
%\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
\title{Fitting convex polyhedra to project 2D bounding box}
\author{Vikas Dhiman\\
  University of Michigan\\
  Ann Arbor, MI, USA\\
{\tt\small dhiman@umich.edu}
\and
Manmohan Chandraker\\
NEC Laboratories America, Inc.\\
Cupertino, CA, USA\\
{\tt\small manu@nec-labs.com}
\and
Jason J Corso\\
  University of Michigan\\
  Ann Arbor, MI, USA\\
{\tt\small jjcorso@eecs.umich.edu}
}
\maketitle

\section{Supplementary Material}
\subsection{Analytic initialization}
Problem: given detection bounding box and ground plane estimate the unknown parameters i.e. position, orientation and size of the car. This problem is under-determined. Given the bounding box, we just have four constraints while we have six unknowns. To reduce the number of unknowns we assume that detection also gives us an estimate of angle and we assume that length of car is 1.3 times the height. Now, we have 4 unknowns and 4 constraints and we can solve them analytically.

\subsubsection{Necessary transforms}
Let the ground plane be known with parameters $(\uv{n}, h)$. Let us take the ground plane to be the XY plane with Z axis pointing upwards and origin at the point of intersection of Y-axis with ground plane. The unit vector describing the ground plane is ambiguous by sign, we choose the sign of $\uv{n}$ such that $\hat{n}_2 > 0$, i.e. the unit vector is along the positive Y-axis of the camera based on the assumption that the camera axis are approximately aligned such that Y-axis points downwards and Z-axis to the front.

@@

\subsubsection{System of equations}
Let the detected bounding box be represented by $[\xmin, \ymin, \xmax, \ymax]^T$. Let $^cT_t$ be the transformation from tracklet to camera.
\newcommand{\Cu}{C_u}
\newcommand{\Cc}{C_c}
\begin{align}
  \Cu &= \begin{bmatrix}
    0.5 & 0.5 & 0\\
    0.5 & -0.5 & 0\\
    -0.5 & -0.5 & 0\\
    -0.5 & 0.5 & 0\\
    0.5 & 0.5 & 1\\
    0.5 & -0.5 & 1\\
    -0.5 & -0.5 & 1\\
    -0.5 & 0.5 & 1
  \end{bmatrix}\\
  C_i &= \diag( C_{u\{i,:\}} ) \begin{bmatrix}3& 0\\0 & 1 \\1 & 0\end{bmatrix} 
\end{align}

@@

\subsubsection{Approximate solution}
Initial approximate solution can be obtained by assuming that $\ymax$ is the projection either of point 
\begin{align}
  \lambda_c \mathbf{u}_c &= \Ptc[0, 0, \frac{h}{2}]^\top + \Pgc \ttg + K\tgc
\end{align}

@@

\subsubsection{Correspondence of bounding box limits to cuboid corners}
The $\xmin$ of bounding can be projection of either of the 8 points of the
cuboid. Once $\xmin$ is chosen the $\xmax$ can be limited to the remain 7
points hence $8 \times 7= 56$ possibilities and similarly $\ymin$ and $\ymax$
lead to 56 different possibilities. In this relatively unconstrained
configuration we have around $56 \times 56 = 3136$ possibilities, which is not
too big but with a little more analysis we can reduce the number. To this
effect we can use the aspect graph of a cuboid to understand the topological
changes by change in view points. Also out of 28 possible configurations in the
aspect graph, we can rule out the configurations that put camera below the
ground plane and directly above the observed car itself. This leaves us with 16
possible topological configurations, which include the symmetrical
configurations when the car is rotated by $180^\circ$. Considering $180^\circ$ symmetry we are only left with 8 possible topological configurations.

@@

\subsection{Numerical integration}
Numerical integration is possible by computed by sampling. Samples need to be
generated from the association probability $\assocP$ for a given $j$. We take
proposal distribution to be a GMM with modes around probable reflection points.
The weights of all Gaussians in the mixture are proportional to the distance of
the point $j$ from projection of ellipsoid centre i.e. 
\begin{align}
  A_{ij} = \frac{1}{Z_j}\exp(-(\trackpj{t} - \mu^i_u)^\top\Sigma_u^i(\trackpj{t} - \mu^i_u))
\end{align}
where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in \eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
The range of Gaussian $G_i$
must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| -
\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| -
\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
\begin{align}
  \PropDist(\lambda) = \sum_i A_{ij} \Gauss(\lambda; \|\relp{i}{t}\| -
  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
\end{align}
And the numerical integral with $K$ samples is computed by
\begin{align}
    \int_1^{\infty}
    \assocP
    \Ereproj(\lambda)
    d\lambda
    =
    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
\end{align}
where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.

\subsection{Sigma of ellipsoid}
\label{sec:sigmacomputation}

@@

\subsection{Projection of ellipsoid to image}
\newcommand{\mubar}{\bar{\mu}_i}
The perspective projection of an ellipsoid in general is not an ellipsoid in
general. We approximate the projection of ellipsoid by projecting a slice
through the ellipsoid. We choose the slice as the plane perpendicular to the
line joining the center of ellipsoid to the optical center of camera. Let
$\muic$ and $\Sigmaicf$ be the parameters of ellipsoid describing the ellipsoid
in camera coordinates. The any point $x$ on the plane satisfies
$x^\top\frac{\muic}{\|\muic\|} = \|\muic\|$. We introduce 
$\mubar = \frac{\muic}{\|\muic\|^2}$ for notational simplicity. Hence, we want
to project the points that satisfy both the equation of chosen plane and the 
ellipsoid i.e.
\begin{align}
  \mubar^\top x = x^\top\mubar &= 1\\ 
  (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \enspace.
\end{align}
We rewrite $\muic = \muic\mubar^\top x$, and $1 = x^\top\mubar \mubar^\top x$
\begin{align}
  (x-\muic\mubar^\top x)^\top\Sigmaicf(x-\muic\mubar^\top x) &= x^\top\mubar \mubar^\top x \enspace,
\end{align}
which is equivalent to 
\begin{align}
  x^\top\left((I-\muic\mubar^\top)^\top\Sigmaicf(I-\muic\mubar^\top) - \mubar \mubar^\top\right)x &= 0\enspace.
\end{align}

@@

\begin{comment}
  \subsection{Bounding box energy}
  \label{sec:totalBBoxEnergy}
  With abuse of notation we represent the four sides of hypothesized bounding
  box by $\projectionOf{\dimsn{i}}$ and detected bounding box by $\bb{i}$.
  Suppose the bounding box $i$ is occluded by bounding box $i$ then the
  bounding box energy becomes a pairwise term.

@@

  \subsubsection{Visible faces from bounding boxes}

@@

\begin{comment}
  \subsubsection{Occlusion mask}
  % Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
  % \begin{itemize}
  %   \item Sort all cars in increasing order of depth
  %   \item for each car $i$ in the sorted list
  %     \begin{itemize}
  %       \item Update mask polygon: \\
  %         $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\dimsn{i}}$
  %       \item $d = \relpz{i}{t}$
  %     \end{itemize}
  % \end{itemize}

@@

  \subsubsection{Algorithm to get faces based occlusion mask}
  \label{sec:occlusionMaskFromOptVector}

@@

  \subsubsection{Visibility fraction of a side}
  Let the center of the projected hypothesized bounding box be $\centerProj$ and
  the four corners be $\{\cornerProj{k}\}_{k=1}^{4}$ . Each side and the center
  of the bounding box form a triangle, for example $\triangleProj{1,2} =
  \{\cornerProj{1}, \cornerProj{2}, \centerProj\}$. We take the visibility of
  this triangle as a visibility of the side $s = (1,2)$. Hence the visibility
  fraction of side is given by
  \begin{align}
    \rho^{ijs}(t) = \frac{\|\triangleProj{s} \setminus \occ{\relpz{i}{t}}\|}
                         {\|\triangleProj{s}\|}
     \label{eq:bboxEnergyFromOccMask}
  \end{align}
\end{comment}

\begin{comment}
  \subsection{Occlusion free projection}
  Occlusion free projection can be obtained by applying the precomputed occlusion
  mask to the face projection.
  \begin{align}
    \occFreeProj{\face} &= \projectionOf{\face} \setminus
    \occ{\relpz{i}{t}}
  \end{align}

  \subsection{Perspective-visibility fraction}

@@

  \section{Uncertainty addition in measurement}
  Consider that we have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
  affect of uncertainty on mean and variance of existing observations. On adding
  noise $[\Delta x, \Delta y]^\top$ with zero mean and covariance $\Delta
  \Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
  \begin{multline}
    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) \\
    + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
  \end{multline}
  where the terms $E(x \Delta x^\top)$ denote the correlation between the data
  vector and the uncertainty in the data. Although we understand that in our case
  the data is the appearance based detection score and uncertainty because of
  occlusion is closely related to the appearance and hence detection score, we
  assume independence between $x$ and $\Delta x$. Hence our resultant covariance
  matrix $ E((x + \Delta x)(x+\Delta x)^\top) = \Sigma + \Delta \Sigma$
  are 4D. But that should not be a problem because the detection scores are
  modeled as $[x_{\text{min}}, y_{\text{min}}, x_{\text{max}},
  y_{\text{max}}]^\top$, we can stack the vectors in the soft occlusion region
  domain as the regions are independent of min or max variation. The parameters
  of 4D occlusion distribution are given by

@@

% \subsubsection{Position in lane}
%
% \begin{align}
%   \Energy{plane} &=
%   \min_{j = 0}^{n_l} \text{DIST}(L_j(k), \pos{i}{t})
% \end{align}
%
 % 
 % We normalize it with the confidence in lane positions.
 % 
 % \begin{align}
 %   \Energy{plane} &=
 %   \min_{m = 0}^{n_l} \text{DIST}(L_m(k), \pos{i}{t})
 %   \LaneUncertainty{\pos{i}{t}}
 % \end{align}

%\subsubsection{Orientation within lane}
%\begin{itemize}
%\end{itemize}

@@

\subsection{Collisions}

@@

\subsubsection{Ellipse-ellipse intersection}
\label{sec:ellipseintersection}
A rectangle with sides $2a$ and $2b$ can be approximated by an ellipse with
equation $\frac{x^2}{a^2} + \frac{y^2}{b^2} = 1$. But this ellipse is inside
the rectangle. To enclose the rectangle, scale the ellipse by a factor of
$\sqrt{2}$. The equation becomes, $\frac{x^2}{2a^2} + \frac{y^2}{2b^2} = 1$.
For rotation $\psi$ and center $\pos{i}{t}$, the equation of ellipse can be
re-written as:
\begin{align}
  (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) &= 1
\end{align}
where
\begin{align}
  \Sigma_i^{-1} &= \begin{bmatrix}
    \frac{\cos^2{\psi}}{2a^2} + \frac{\sin^2{\psi}}{2b^2} &
    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2})\\
    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2}) &
    \frac{\sin^2{\psi}}{2a^2} + \frac{\cos^2{\psi}}{2b^2} \\
  \end{bmatrix}
\end{align}

@@

\subsubsection{Smoother collision probability}
\label{sec:smoothercollision}
%The above mentioned ellipse-ellipse intersection formulation gives us an
%insight: the distance between two oriented ellipse boundaries can be again
%formulated as a distance metric\footnote{TODO:proof}.
Instead of using Gaussians to model
collision constraints as done by \cite{milan2013continuous}, we use a more
steeper sigmoid function.
\begin{multline}
  \EnergyCol = \frac{1}{1 +
\exp(-k(\pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t})-1)}\\
\frac{1}{1 +
\exp(-k(\pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t})-1)}
\end{multline}
where $k$ is steepness parameter.
%$d(.)$ is the distance metric defined as:
%\begin{multline}
%  d(\pos{i}{t}, \dimsn{i}, \pos{j}{t}, \dimsn{j})
%  =
%  \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t} \\
%  + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
%  - \mu_c^\top\Sigma_c^{-1}\mu_c
%\end{multline}

@@

% \subsection{Object detection score}
% \begin{align}
% \Energy{det}(\relp{i}{t}, \dimsn{i}) = 
%              \frac{1}{S_t^2(\projectionOf{\dimsn{i}})}
% \end{align}

>>>>

\section{Analytic initialization}
Problem: given detection bounding box and ground plane estimate the unknown parameters i.e. position, orientation and size of the car. This problem is under-determined. Given the bounding box, we just have four constraints while we have six unknowns. To reduce the number of unknowns we assume that detection also gives us an estimate of angle and we assume that length of car is 1.3 times the height. Now, we have 4 unknowns and 4 constraints and we can solve them analytically.

\subsection{Necessary transforms}
Let the ground plane be known with parameters $(\uv{n}, h)$. Let us take the ground plane to be the XY plane with Z axis pointing upwards and origin at the point of intersection of Y-axis with ground plane. The unit vector describing the ground plane is ambiguous by sign, we choose the sign of $\uv{n}$ such that $\hat{n}_2 > 0$, i.e. the unit vector is along the positive Y-axis of the camera based on the assumption that the camera axis are approximately aligned such that Y-axis points downwards and Z-axis to the front.

@@

\subsection{System of equations}
Let the detected bounding box be represented by $[\xmin, \ymin, \xmax, \ymax]^T$. Let $^cT_t$ be the transformation from tracklet to camera.
\newcommand{\Cu}{C_u}
\newcommand{\Cc}{C_c}
\begin{align}
  \Cu &= \begin{bmatrix}
    0.5 & 0.5 & 0\\
    0.5 & -0.5 & 0\\
    -0.5 & -0.5 & 0\\
    -0.5 & 0.5 & 0\\
    0.5 & 0.5 & 1\\
    0.5 & -0.5 & 1\\
    -0.5 & -0.5 & 1\\
    -0.5 & 0.5 & 1
  \end{bmatrix}\\
  C_i &= \diag( C_{u\{i,:\}} ) \begin{bmatrix}3& 0\\0 & 1 \\1 & 0\end{bmatrix} 
\end{align}

@@

\subsection{Approximate solution}
Initial approximate solution can be obtained by assuming that $\ymax$ is the projection either of point 
\begin{align}
  \lambda_c \mathbf{u}_c &= \Ptc[0, 0, \frac{h}{2}]^\top + \Pgc \ttg + K\tgc
\end{align}

@@

\subsection{Correspondence of bounding box limits to cuboid corners}
The $\xmin$ of bounding can be projection of either of the 8 points of the
cuboid. Once $\xmin$ is chosen the $\xmax$ can be limited to the remain 7
points hence $8 \times 7= 56$ possibilities and similarly $\ymin$ and $\ymax$
lead to 56 different possibilities. In this relatively unconstrained
configuration we have around $56 \times 56 = 3136$ possibilities, which is not
too big but with a little more analysis we can reduce the number. To this
effect we can use the aspect graph of a cuboid to understand the topological
changes by change in view points. Also out of 28 possible configurations in the
aspect graph, we can rule out the configurations that put camera below the
ground plane and directly above the observed car itself. This leaves us with 16
possible topological configurations, which include the symmetrical
configurations when the car is rotated by $180^\circ$. Considering $180^\circ$ symmetry we are only left with 8 possible topological configurations.

@@

\section{Numerical integration}
Numerical integration is possible by computed by sampling. Samples need to be
generated from the association probability $\assocP$ for a given $j$. We take
proposal distribution to be a GMM with modes around probable reflection points.
The weights of all Gaussians in the mixture are proportional to the distance of
the point $j$ from projection of ellipsoid centre i.e. 
\begin{align}
  A_{ij} = \frac{1}{Z_j}\exp(-(\trackpj{t} - \mu^i_u)^\top\Sigma_u^i(\trackpj{t} - \mu^i_u))
\end{align}
where $Z_j = \sum_{i=1}^N A_{ij}$ and $\mu^i_u$ and $\Sigma_u^i$ are described in \eqref{eq:muiudef} and \eqref{eq:sigmauidef} respectively.
The range of Gaussian $G_i$
must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| -
\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| -
\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
\begin{align}
  \PropDist(\lambda) = \sum_i A_{ij} \Gauss(\lambda; \|\relp{i}{t}\| -
  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
\end{align}
And the numerical integral with $K$ samples is computed by
\begin{align}
    \int_1^{\infty}
    \assocP
    \Ereproj(\lambda)
    d\lambda
    =
    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
\end{align}
where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.

\section{Sigma of ellipsoid}
\label{sec:sigmacomputation}

@@

\section{Projection of ellipsoid to image}
\newcommand{\mubar}{\bar{\mu}_i}
The perspective projection of an ellipsoid in general is not an ellipsoid in
general. We approximate the projection of ellipsoid by projecting a slice
through the ellipsoid. We choose the slice as the plane perpendicular to the
line joining the center of ellipsoid to the optical center of camera. Let
$\muic$ and $\Sigmaicf$ be the parameters of ellipsoid describing the ellipsoid
in camera coordinates. The any point $x$ on the plane satisfies
$x^\top\frac{\muic}{\|\muic\|} = \|\muic\|$. We introduce 
$\mubar = \frac{\muic}{\|\muic\|^2}$ for notational simplicity. Hence, we want
to project the points that satisfy both the equation of chosen plane and the 
ellipsoid i.e.
\begin{align}
  \mubar^\top x = x^\top\mubar &= 1\\ 
  (x-\muic)^\top\Sigmaicf(x-\muic) &= 1 \enspace.
\end{align}
We rewrite $\muic = \muic\mubar^\top x$, and $1 = x^\top\mubar \mubar^\top x$
\begin{align}
  (x-\muic\mubar^\top x)^\top\Sigmaicf(x-\muic\mubar^\top x) &= x^\top\mubar \mubar^\top x \enspace,
\end{align}
which is equivalent to 
\begin{align}
  x^\top\left((I-\muic\mubar^\top)^\top\Sigmaicf(I-\muic\mubar^\top) - \mubar \mubar^\top\right)x &= 0\enspace.
\end{align}

@@

\begin{comment}
  \section{Bounding box energy}
  \label{sec:totalBBoxEnergy}
  With abuse of notation we represent the four sides of hypothesized bounding
  box by $\projectionOf{\dimsn{i}}$ and detected bounding box by $\bb{i}$.
  Suppose the bounding box $i$ is occluded by bounding box $i$ then the
  bounding box energy becomes a pairwise term.

@@

  \subsection{Visible faces from bounding boxes}

@@

\begin{comment}
  \subsection{Occlusion mask}
  % Initialize empty mask polygon $\occ{0}$ at depth $d=0$.
  % \begin{itemize}
  %   \item Sort all cars in increasing order of depth
  %   \item for each car $i$ in the sorted list
  %     \begin{itemize}
  %       \item Update mask polygon: \\
  %         $\occ{\relpz{i}{t}} = \occ{d} \cup \projectionOf{\dimsn{i}}$
  %       \item $d = \relpz{i}{t}$
  %     \end{itemize}
  % \end{itemize}

@@

  \subsection{Algorithm to get faces based occlusion mask}
  \label{sec:occlusionMaskFromOptVector}

@@

  \subsection{Visibility fraction of a side}
  Let the center of the projected hypothesized bounding box be $\centerProj$ and
  the four corners be $\{\cornerProj{k}\}_{k=1}^{4}$ . Each side and the center
  of the bounding box form a triangle, for example $\triangleProj{1,2} =
  \{\cornerProj{1}, \cornerProj{2}, \centerProj\}$. We take the visibility of
  this triangle as a visibility of the side $s = (1,2)$. Hence the visibility
  fraction of side is given by
  \begin{align}
    \rho^{ijs}(t) = \frac{\|\triangleProj{s} \setminus \occ{\relpz{i}{t}}\|}
                         {\|\triangleProj{s}\|}
     \label{eq:bboxEnergyFromOccMask}
  \end{align}
\end{comment}

\begin{comment}
  \section{Occlusion free projection}
  Occlusion free projection can be obtained by applying the precomputed occlusion
  mask to the face projection.
  \begin{align}
    \occFreeProj{\face} &= \projectionOf{\face} \setminus
    \occ{\relpz{i}{t}}
  \end{align}

  \section{Perspective-visibility fraction}

@@

  \section{Uncertainty addition in measurement}
  Consider that we have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
  affect of uncertainty on mean and variance of existing observations. On adding
  noise $[\Delta x, \Delta y]^\top$ with zero mean and covariance $\Delta
  \Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
  \begin{align}
    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) %\\
    + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
  \end{align}
  where the terms $E(x \Delta x^\top)$ denote the correlation between the data
  vector and the uncertainty in the data. Although we understand that in our case
  the data is the appearance based detection score and uncertainty because of
  occlusion is closely related to the appearance and hence detection score, we
  assume independence between $x$ and $\Delta x$. Hence our resultant covariance
  matrix $ E((x + \Delta x)(x+\Delta x)^\top) = \Sigma + \Delta \Sigma$
  are 4D. But that should not be a problem because the detection scores are
  modeled as $[x_{\text{min}}, y_{\text{min}}, x_{\text{max}},
  y_{\text{max}}]^\top$, we can stack the vectors in the soft occlusion region
  domain as the regions are independent of min or max variation. The parameters
  of 4D occlusion distribution are given by

@@

% \subsection{Position in lane}
%
% \begin{align}
%   \Energy{plane} &=
%   \min_{j = 0}^{n_l} \text{DIST}(L_j(k), \pos{i}{t})
% \end{align}
%
 % 
 % We normalize it with the confidence in lane positions.
 % 
 % \begin{align}
 %   \Energy{plane} &=
 %   \min_{m = 0}^{n_l} \text{DIST}(L_m(k), \pos{i}{t})
 %   \LaneUncertainty{\pos{i}{t}}
 % \end{align}

%\subsection{Orientation within lane}
%\begin{itemize}
%\end{itemize}

@@

\section{Collisions}

@@

\subsection{Ellipse-ellipse intersection}
\label{sec:ellipseintersection}
A rectangle with sides $2a$ and $2b$ can be approximated by an ellipse with
equation $\frac{x^2}{a^2} + \frac{y^2}{b^2} = 1$. But this ellipse is inside
the rectangle. To enclose the rectangle, scale the ellipse by a factor of
$\sqrt{2}$. The equation becomes, $\frac{x^2}{2a^2} + \frac{y^2}{2b^2} = 1$.
For rotation $\psi$ and center $\pos{i}{t}$, the equation of ellipse can be
re-written as:
\begin{align}
  (\mathbf{x} - \pos{i}{t})^\top\Sigma_i^{-1}(\mathbf{x} - \pos{i}{t}) &= 1
\end{align}
where
\begin{align}
  \Sigma_i^{-1} &= \begin{bmatrix}
    \frac{\cos^2{\psi}}{2a^2} + \frac{\sin^2{\psi}}{2b^2} &
    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2})\\
    \frac{\cos{\psi}\sin{\psi}}{2}(\frac{1}{b^2} - \frac{1}{a^2}) &
    \frac{\sin^2{\psi}}{2a^2} + \frac{\cos^2{\psi}}{2b^2} \\
  \end{bmatrix}
\end{align}

@@

\subsection{Smoother collision probability}
\label{sec:smoothercollision}
%The above mentioned ellipse-ellipse intersection formulation gives us an
%insight: the distance between two oriented ellipse boundaries can be again
%formulated as a distance metric\footnote{TODO:proof}.
Instead of using Gaussians to model
collision constraints as done by \cite{milan2013continuous}, we use a more
steeper sigmoid function.
\begin{multline}
  \EnergyCol = \frac{1}{1 +
\exp(-k(\pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t})-1)}\\
\frac{1}{1 +
\exp(-k(\pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t})-1)}
\end{multline}
where $k$ is steepness parameter.
%$d(.)$ is the distance metric defined as:
%\begin{multline}
%  d(\pos{i}{t}, \dimsn{i}, \pos{j}{t}, \dimsn{j})
%  =
%  \pos{i}{t}^\top\Sigma_i^{-1}\pos{i}{t} \\
%  + \pos{j}{t}^\top\Sigma_j^{-1}\pos{j}{t}
%  - \mu_c^\top\Sigma_c^{-1}\mu_c
%\end{multline}

@@

% \section{Object detection score}
% \begin{align}
% \Energy{det}(\relp{i}{t}, \dimsn{i}) = 
%              \frac{1}{S_t^2(\projectionOf{\dimsn{i}})}
% \end{align}
